---
title: "DSCI 521 Lab4 Presentation - "
format: revealjs
editor: visual
---

## Sing the song ! {transition="fade"}

Never gonna give you up\
Never gonna let you down\
Never gonna run around and desert you\
\
Never gonna make you cry\
Never gonna say goodbye\
Never gonna tell a lie and hurt you\

------------------------------------------------------------------------

## Now calculate how many words are in these lyrics {transition="zoom"}

```{r echo =TRUE}
x = "Never gonna give you up
Never gonna let you down
Never gonna run around and desert you
Never gonna make you cry
Never gonna say goodbye
Never gonna tell a lie and hurt you"

word_count <- lengths((strsplit(x,"\\W"))[1])

paste0("These lyrics have ",word_count, " words" )

```

------------------------------------------------------------------------

## Time to do math!

Now stop singing and study math!

------------------------------------------------------------------------
## Math Task

We will create a function that gives us the sum , difference, product and division of 2 numbers!

```{r echo=TRUE}
math_fun <- function(x,y){
  s = x+y
  d = x-y
  p = x*y
  r = x/y
  paste0("Sum = ",s, " Difference = ",d," Product = ",p, " Division = ",r)
}
math_fun(20,10)
```

Now you can go back to singing :)
